D3064R0: OOTA Execution on Real Implementations is Provably Vacuous

### 2023-12-21 ootavacuous.tex
Self-review in sending initial December 19 email to Alan
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>
Call out "no invented load" in filename
Reported-by: Alan Stern <stern@rowland.harvard.edu>
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>
Add intermediate three-thread whyrfe litmus tests
Reported-by: Alan Stern <stern@rowland.harvard.edu>
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Listing~\ref{lst:Why rfe Instead of Tried-And-True rf?}
revises
Listing~\ref{lst:Three-Process Version of JMM Causality Test Case 4}
to flatten \co{PO()} and \co{P1()} into a single thread, so that the
resulting \co{P0()} has an rfi link instead of an rfe link connecting
the store to and load from \co{y}.
In addition, the value stored to \co{y} is forced to be at least the
value 17, and the value stored to \co{z} is forced to be at most the
value 17.
This of course means that the store to \co{z} must always be the value
17, and that a C++ implementation could prove this by examining \co{P0()}
in isolation given that it is also legal for a C++ implementation
to replace the value loaded from \co{y} with the value just stored.\footnote{
	This is not an option in C because atomic operations are volatile,
	and thus observed behavior.}

@@

\begin{listing}[tbp]
@@ DisplayRunLitmus litmus/oota-invented-load.litmus @@
\caption{Inventing Atomic Loads}
\label{lst:Inventing Atomic Loads}
\end{listing}

@@

% @@@ TODO:

>>>>

Listing~\ref{lst:Why rfe Instead of Tried-And-True rf?}
revises
Listing~\ref{lst:Three-Process Version of JMM Causality Test Case 4}
so that the value stored to \co{y} is forced to be at most the
value 17, and the value stored to \co{z} is forced to be at least the
value 17.
This of course means that the store to \co{z} must always be the value
17, as can be seen from the \co{herd7} output.
However, a single-thread-at-a-time analysis could not prove this.

\begin{listing}[tbp]
@@ DisplayRunLitmus litmus/oota-whyrfe-3.litmus @@
\caption{Three-Process Version of JMM Causality Test Case 4 With Max and Min}
\label{lst:Three-Process Version of JMM Causality Test Case 4 With Max and Min}
\end{listing}

Listing~\ref{lst:Why rfe Instead of Tried-And-True rf?}
further revises
Listing~\ref{lst:Three-Process Version of JMM Causality Test Case 4 With Max and Min}
to flatten \co{PO()} and \co{P1()} into a single thread, so that the
resulting \co{P0()} has an rfi link instead of an rfe link connecting
the store to and load from \co{y}.
This means that a C++ implementation could prove that the value 17 is
always stored to \co{z} by examining \co{P0()} in isolation, given that
it is also legal for a C++ implementation to replace the value loaded
from \co{y} with the value just stored.\footnote{
	This is not an option in C because atomic operations are volatile,
	and thus observed behavior.}

@@

\begin{listing}[tbp]
@@ DisplayRunLitmus litmus/oota-no-invented-load.litmus @@
\caption{Inventing Atomic Loads}
\label{lst:Inventing Atomic Loads}
\end{listing}

@@

% @@@ TODO:
% Construct interleaved OOTA examples (see sheets of paper).
% Construct nondeterminism example, for example, based on i++.
% Check cmbc on nondeterministic i++.
% Use LKMM as check for dependencies?  Check invented-load litmus tests.
